### 2015-02-16 lessonplans/hmwkch5.tex
populating the first few homeworks

\begin{enumerate}
\item What proportion of all test takers will have a GRE Verbal score above 600 points?\\[1in]
\item What proportion of all test takers will have a GRE Verbal score below 375 points?\\[1in]
\item What proportion of all test takers will have a GRE Verbal score between 500 and 700 points?\\[1in]
\item What GRE Verbal score will 40\% of all test takers score below?\\[1in]
\item What GRE verbal score will 10\% of all test takers score above?
\end{enumerate}

\newpage

\item In a study to determine the nature of the relationship between heart rates and body temperature, body temperatures were collected from 130 individuals. The body temperatures, in degrees Fahrenheit, can be found in the JMP data file {\bf samplebodytemps.JMP} in Blackboard.

Use JMP to determine if the distribution of body temperatures can be modeled with a normal model. Make sure to turn in the output from JMP with your assignment. In your answer, make sure to use information from the JMP output that supports your conclusions.

>>>>

\begin{enumerate}
\item What proportion of all test takers will have a GRE Verbal score above 600 points?\\%[1in]
\item What proportion of all test takers will have a GRE Verbal score below 375 points?\\%[1in]
\item What proportion of all test takers will have a GRE Verbal score between 500 and 700 points?\\%[1in]
\item What GRE Verbal score will 40\% of all test takers score below?\\%[1in]
\item What GRE verbal score will 10\% of all test takers score above?
\end{enumerate}

%\newpage

\item In a study to determine the nature of the relationship between heart rates and body temperature, body temperatures were collected from 130 individuals. The body temperatures, in degrees Fahrenheit, can be found in the  data file {\bf samplebodytemps.csv} in Blackboard.

Use the intRo software to determine if the distribution of body temperatures can be modeled with a normal model. Make sure to turn in the output from intRo with your assignment. In your answer, make sure to use information from the computer output that supports your conclusions.

### 2015-02-16 lessonplans/hmwkch6-7.tex
populating the first few homeworks

\vspace{2.5in}

\item Which two variables have the strongest correlation? What is it?

\vspace{1in}

\item Make scatterplots of each of the pairs of variables (don't hand these in). Write a paragraph briefly describing the associations, and discussing whether correlation is  or isn't an appropriate summary.

\end{enumerate}

>>>>

%\vspace{2.5in}

\begin{enumerate}
\item Which two variables have the strongest correlation? What is it?

%\vspace{1in}

\item Make scatterplots of each of the pairs of variables (don't hand these in). Write a paragraph briefly describing the associations, and discussing whether correlation is  or isn't an appropriate summary.
\end{enumerate}

\item Fit a regression model for SalePrice against LivingArea.

\begin{enumerate}
\item Write out the model. 
\item Print the scatterplot and sketch the linear model on this plot. 
\item What proportion of variation in house price does the living area explain?
\item
Predict the average sales price for a house having 1500 sq ft of living space.
\item There is a (small) problem with the fit. Diagnose this using the residual plots, and write a paragraph on how you would correct it, and re-fit the model. 
\end{enumerate}
\end{enumerate}
